Estimating Life-Stage Specific Habitat Capacity for Anadromous Salmonids using Quantile Random Forest Models

### 2019-12-10 analysis/paper/paper.Rmd
try using data objects created in QRFpaper repo.

```{r packages}
library(tidyverse)
library(QRFcapacity) # for the moment, until we know exactly what data to copy over to this repo
library(janitor)
library(knitr)

@@

>>>>

```{r packages}
library(tidyverse)
library(QRFcapacity) # for the moment, until we know exactly what data to copy over to this repo
library(QRFpaper)
library(janitor)
library(knitr)

@@

```{r load-data}
data(fish_hab, 
     hab_dict, 
     hab_data, 
     hab_avg, 
     qrf_data,
     dens_offset,
     qrf_mod,
     sel_hab_mets)
```
